PANCHANGE_analysis

### 2021-01-13 PANCHANGE_analysis.Rmd
fixed prepandemic regression models

# GAD prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

@@

# PHQ prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

@@

# OCIR prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

>>>>

# GAD prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

# Regression diagnostic statistics
gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_reg_stats)
gad_prepan_model1b_education_reg_stats
```

@@

# PHQ prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

# Regression diagnostic statistics
phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_reg_stats)
phq_prepan_model1b_education_reg_stats
```

@@

# OCIR prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_reg_stats)
ocir_prepan_model1b_education_reg_stats
```
